Motional Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material

### 2018-04-17 sm.tex
sm update from Kang-Kuen

\newpage
\subsubsection{Group 4}
This group is repeated 7 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-3&$18.858$&$18.605$&70.2&$2\pi\times16$&F2\\\hline
    $x$&-2&$19.625$&$18.649$&44.1&$2\pi\times23$&F1\\\hline
    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
    $y$&-2&$19.615$&$18.648$&28.6&$2\pi\times35$&F1\\\hline
    $z$&-3&$18.858$&$18.605$&70.2&$2\pi\times16$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 5}
This group is repeated 10 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
    $z$&-1&$18.685$&$18.605$&52.5&$2\pi\times16$&F2\\\hline
    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&70.0&$2\pi\times23$&F1\\\hline
    $z$&-1&$18.685$&$18.605$&52.5&$2\pi\times16$&F2\\\hline
    $y$&-1&$19.130$&$18.648$&46.0&$2\pi\times35$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 6}
This group is repeated 30 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-1&$18.683$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
    $z$&-1&$18.683$&$18.605$&135.0&$2\pi\times11$&F2\\\hline
    $z$&-1&$18.685$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
    $z$&-1&$18.685$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
    $z$&-1&$18.685$&$18.605$&135.0&$2\pi\times11$&F2\\\hline
    $z$&-1&$18.685$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&70.0&$2\pi\times23$&F1\\\hline
    $y$&-1&$19.130$&$18.648$&46.0&$2\pi\times35$&F1\\\hline
  \end{tabular}
\end{center}

>>>>

\newpage
\subsubsection{Group 4}
This group is repeated 7 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-3&$18.858$&$18.605$&70.2&$2\pi\times16$&F2\\\hline
    $x$&-2&$19.625$&$18.649$&44.1&$2\pi\times23$&F1\\\hline
    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
    $y$&-2&$19.615$&$18.648$&28.6&$2\pi\times35$&F1\\\hline
    $z$&-3&$18.858$&$18.605$&70.2&$2\pi\times16$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 5}
This group is repeated 10 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
    $z$&-1&$18.685$&$18.605$&52.5&$2\pi\times16$&F2\\\hline
    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&70.0&$2\pi\times23$&F1\\\hline
    $z$&-1&$18.685$&$18.605$&52.5&$2\pi\times16$&F2\\\hline
    $y$&-1&$19.130$&$18.648$&46.0&$2\pi\times35$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 6}
This group is repeated 30 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-1&$18.683$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
    $z$&-1&$18.683$&$18.605$&135.0&$2\pi\times11$&F2\\\hline
    $z$&-1&$18.685$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
    $z$&-1&$18.685$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
    $z$&-1&$18.685$&$18.605$&135.0&$2\pi\times11$&F2\\\hline
    $z$&-1&$18.685$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&70.0&$2\pi\times23$&F1\\\hline
    $y$&-1&$19.130$&$18.648$&46.0&$2\pi\times35$&F1\\\hline
  \end{tabular}
\end{center}
\newpage

\section{Zoomed data for Raman Sideband Cooling}
Efficient RSC enables the preparation of single atoms with a high probability of being in the trap ground state.  That probability can be measured by Raman sideband spectroscopy.
Here we show a zoomed spectra after RSC for clarity.  The cooling orders ($\Delta n=-1,-2$ for radial x and y axes and $\Delta n=-1, \dots, -5$ for axial z axis) are shown.
Each data point comes from repeated measurements with more than 450 single atoms loaded.
The heights of these sidebands are about $2.5\%$. \\

\includegraphics[height=4cm]{spectrum_zoom_cool_rx.pdf}
\includegraphics[height=4cm]{spectrum_zoom_cool_ry.pdf}
\includegraphics[height=4cm]{spectrum_zoom_cool_az.pdf}
